A dynamic bioenergetic model for coral-*Symbiodinium* symbioses and coral bleaching as an alternate stable state

### 2017-03-22 JTB_ms/JTB_ms.Rmd
formatting

![Alternate stable states in S:H biomass and growth across a light gradient. Alternate stable states occur between ~25-42 mol photons m^-2^ d^-1^ under these conditions (DIN=1e-7 molN L^-1^; X=1e-7 CmolX L^-1^), depending on whether initial S:H is high (1, closed circles), representing a healthy coral, or low (0.0001, open circles), representing a bleached coral. Arrow above point at L=25 indicates a S:H ratio beyond the axis range; this 'overshoot' phenomenon, in which initially  bleached corals may achieve high S:H ratios while remaining in a carbon-limited state is discussed in the *Coral Bleaching and Recovery* section.](../img/Fig2.png)

>>>>

![Alternate stable states in S:H biomass and growth across a light gradient. Alternate stable states occur between ~25-42 mol photons m^-2^ d^-1^ under these conditions (DIN=1e-7 mol N L^-1^; X=1e-7 C-mol X L^-1^), depending on whether initial S:H is high (1, closed circles), representing a healthy coral, or low (0.0001, open circles), representing a bleached coral. Arrow above point at L=25 indicates a S:H ratio beyond the axis range; this 'overshoot' phenomenon, in which initially  bleached corals may achieve high S:H ratios while remaining in a carbon-limited state is discussed in the *Coral Bleaching and Recovery* section.](../img/Fig2.png)
